---
title: "Senior Project"
output:
  html_document:
    df_print: paged
---

Load all the packages we need 

```{r}
library(readxl)
library(tidyverse)
library(RColorBrewer)
library(ggplot2)
library(ggthemes)
library(dplyr)
library(choroplethr)
library(choroplethrMaps)
library(ggbeeswarm)
library(tidyverse)
library(lubridate)
library(plotly)
library(ggbeeswarm)

```
 
load all the data we are going to use here and do summary of each dataset.

Summary statistics such as mean,median,mode and quartiles for each variable.
 
```{r}


COR_Adult_CCcontact <- read_excel("COR_Adult_CCcontact.xlsx")
summary(COR_Adult_CCcontact) 

MS_ADO_AEM <- read_excel("MS_ADO_AEM.xlsx")
summary(MS_ADO_AEM) 

MS_ADO_MCS_Alien <- read_excel("MS_ADO_MCS_Alien.xlsx")
summary(MS_ADO_MCS_Alien) 

MS_ADO_Total <- read_excel("MS_ADO_Total.xlsx")
summary(MS_ADO_Total) 

MS_ADO_QMB <- read_excel("MS_ADO_QMB.xlsx")
summary(MS_ADO_QMB) 

ESA_TANF_Child_Only <- read_excel("ESA_TANF_Child_Only.xlsx")
summary(ESA_TANF_Child_Only)

#To not see any number like "1e+05" we will penalize the scientific notation version by 999

options(scipen=999)
```
 
 
 let's have a first look at the data using ggplot2.


We have used Caseload as a constant element in all graphics for the x axis and we have used ActualValue, ForecastValue, and Variance for the y axis for each dataset we did load here 

```{r}


ESA_TANF_Child_Only  %>% ggplot(aes(x=Caseload,y=ActualValue)) + geom_line() + geom_hline(yintercept = 0,color="purple")

```

 Use span to control the "wiggliness" of the default loess smoother.
 The span is the fraction of points used to fit each local regression.
 small numbers make a wigglier curve, larger numbers make a smoother curve.
 
 We added a loess smoothing curve. The span of .05 is the result of trial and error to give us the degree of smoothing we wanted.
 
```{r}

ESA_TANF_Child_Only  %>% ggplot(aes(x=Caseload,y=ForecastValue)) + geom_line() + geom_hline(yintercept = 0,color="purple")+
  geom_smooth(method = "loess",span=.05)

ESA_TANF_Child_Only  %>% ggplot(aes(x=Caseload,y=Variance)) + geom_line() + geom_hline(yintercept = 0,color="purple")+
  geom_smooth(method = "loess",span=.05)
```



We did use different dataset here.
We made the graph interactive using plotly.

```{r}


spa1 =COR_Adult_CCcontact %>% ggplot(aes(x=Caseload,y=ActualValue)) + geom_line() + geom_hline(yintercept = 0,color="purple")
ggplotly(spa1)


spa2 = COR_Adult_CCcontact %>% ggplot(aes(x=Caseload,y=ForecastValue)) + geom_line() + geom_hline(yintercept = 0,color="purple")+
  geom_smooth(method = "loess",span=.07)
ggplotly(spa2)

spa3 = COR_Adult_CCcontact %>% ggplot(aes(x=Caseload,y=Variance)) + geom_line() + geom_hline(yintercept = 0,color="purple")+
  geom_smooth(method = "loess",span=.07)
ggplotly(spa3)
```


```{r}
spb1 =MS_ADO_AEM %>% ggplot(aes(x=Caseload,y=ActualValue)) + geom_line() + geom_hline(yintercept = 0,color="purple")
ggplotly(spb1)

spb2 =MS_ADO_AEM %>% ggplot(aes(x=Caseload,y=ForecastValue)) + geom_line() + geom_hline(yintercept = 0,color="purple")+
  geom_smooth(method = "loess",span=.2)
ggplotly(spb2)

spb3 =MS_ADO_AEM %>% ggplot(aes(x=Caseload,y=Variance)) + geom_line() + geom_hline(yintercept = 0,color="purple")+
  geom_smooth(method = "loess",span=.2)
ggplotly(spb3)
```

```{r}
spc1=MS_ADO_MCS_Alien %>% ggplot(aes(x=Caseload,y=ActualValue)) + geom_line() + geom_hline(yintercept = 0,color="purple")
ggplotly(spc1)

spc2=MS_ADO_MCS_Alien %>% ggplot(aes(x=Caseload,y=ForecastValue)) + geom_line() + geom_hline(yintercept = 0,color="purple")+
  geom_smooth(method = "loess",span=.2)
ggplotly(spc2)

spc3=MS_ADO_MCS_Alien %>% ggplot(aes(x=Caseload,y=Variance)) + geom_line() + geom_hline(yintercept = 0,color="purple")+
  geom_smooth(method = "loess",span=.2)
ggplotly(spc3)
```

```{r}
spd1=MS_ADO_Total  %>% ggplot(aes(x=Caseload,y=ActualValue)) + geom_line() + geom_hline(yintercept = 0,color="purple")
ggplotly(spd1)

spd2=MS_ADO_Total  %>% ggplot(aes(x=Caseload,y=ForecastValue)) + geom_line() + geom_hline(yintercept = 0,color="purple")+
  geom_smooth(method = "loess",span=.05)
ggplotly(spd2)

spd3=MS_ADO_Total  %>% ggplot(aes(x=Caseload,y=Variance)) + geom_line() + geom_hline(yintercept = 0,color="purple")+
  geom_smooth(method = "loess",span=.05)
ggplotly(spd3)
```

```{r}
spe1=MS_ADO_QMB  %>% ggplot(aes(x=Caseload,y=ActualValue)) + geom_line() + geom_hline(yintercept = 0,color="purple")
ggplotly(spe1)

spe2=MS_ADO_QMB  %>% ggplot(aes(x=Caseload,y=ForecastValue)) + geom_line() + geom_hline(yintercept = 0,color="purple")+
  geom_smooth(method = "loess",span=.2)
ggplotly(spe2)

spe3=MS_ADO_QMB  %>% ggplot(aes(x=Caseload,y=Variance)) + geom_line() + geom_hline(yintercept = 0,color="purple")+
  geom_smooth(method = "loess",span=.2)
ggplotly(spe3)
```







